---
title: "dplyr filter homework"
author: "Kaisa Roots"
date: "2019-03-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises

Loading required libraries:
```{r}
library(tidyverse)
library(lubridate)
library(here)
```

Importing dataset:
```{r}
viruses <- read_csv(here("data", "viruses.csv"))
```

Print out dataset:
```{r}
viruses
```


1. Find all viruses that:

- have genome of over 10000kb

I noticed that the genome size in this data set is marked either as 1.000 kb (with dot separator) or 1000 kb (without separators), hence, I used both variants to filter out genome sizes over 10000 kb.  

```{r}
filter(viruses, size_kb >= 10000 | size_kb >= 10.000)
```

- belong to *Papillomaviridae*

```{r}
filter(viruses, subgroup == "Papillomaviridae")
```

- are from plants and environment

I filter viruses that are either from plants or from the environment. 

```{r}
filter(viruses, host == "plants" | host == "environment")
```

- were released between 01. January 1980 - 01. January 1990, including these days:

```{r}
filter(viruses, release_date >= "1980-01-01", release_date <= "1990-01-01")
```


2. there is also between() function in dplyr. 

What does it do? Run ?between
How can you use it to find viruses with genomes between 1 to 2 kb?

```{r}
?between
```

between() is a shortcut for >= & <=. 

```{r}
filter(viruses, between(size_kb, 1, 2))
```

3. Find Enteroviruses:

Hint: use str_detect()
```{r}
filter(viruses, str_detect(organism_name, "enterovirus"))
```

